---
title: "Document with Glossaries"
author: "Blaine Mooers"
output:
  pdf_document:
    extra_dependencies: ['amsmath', 'minted']
header-includes:
  - \usepackage{helvet}
  - \usepackage{datetime2}
  - \setlength{\parindent}{0pt} % make block paragraphs
  - \usepackage{lastpage}
  - \usepackage{wrapfig}
  - \usepackage{booktabs}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{} % Clear all header and footer fields
  - \fancyhead[L]{\today}
  - \fancyhead[C]{MAB for Project 0000} % Center header
  - \fancyhead[R]{\thepage\ / \pageref{LastPage}}
  - \usepackage{parskip} % add a blank line between paragraphs upon export to PDF.
  - \usepackage{index}
  - \makeindex
  - \bibliographystyle{cell}
  - \renewcommand{\refname}{Literature Cited}
  - \usepackage{bibentry}
  - \nobibliography*
  - \usepackage[acronym]{glossaries}
  - \usepackage[automake]{glossaries-extra}
  - \newglossary[nlg]{notation}{not}{ntn}{Notation}
  - \makeglossaries # must occur before input of the glossaries
  - \loadglsentries{/Users/blaine/glossaries/acronyms}
  - \loadglsentries{/Users/blaine/glossaries/glossary}
  - \loadglsentries{/Users/blaine/glossaries/notation}
  - \newglossaryentry{latex}{ name=LaTeX, description={A document preparation system} }

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
options(tinytex.engine_args = '-shell-escape')
```

\tableofcontents

## Introduction

This document demonstrates how to use the glossaries package in R Markdown.

## Glossary Entries
The term \gls{latex} is commonly used in academic writing \index{LaTeX}.

I enjoy \gls{bda} because \gls{bda} parallels the scientific process \index{BDA}.
\gls{bda} can be extended in application with \acrshort{advi}.
\gls{bda} can be used on \gls{aws}.

\section*{Illustrated and annotated bibliography}
\addcontentsline{toc}{section}{Illustrated and annotated bibliography}

\subsection*{\bibentry{Mooers2020ShortcutsForFasterImageCreationInPyMOL}}
\addcontentsline{toc}{subsection}{Mooers2020ShortcutsForFasterImageCreationInPyMOL}
\input{/Users/blaine/bibNotes/Mooers2020ShortcutsForFasterImageCreationInPyMOL.Rmd}


\subsection*{\bibentry{Mooers2021TemplatesForWritingPyMOLScripts}}
\addcontentsline{toc}{subsection}{Mooers2021TemplatesForWritingPyMOLScripts}
\input{/Users/blaine/bibNotes/Mooers2021TemplatesForWritingPyMOLScripts.Rmd}

\clearpage
\printglossary[type=\acronymtype,title=Acronyms]
\addcontentsline{toc}{section}{Acronyms}

\printglossary[title=Glossary] 
\addcontentsline{toc}{section}{Glossary}

\clearpage
\addcontentsline{toc}{section}{Mathematical Notation}
\glsaddall[types={notation}] % add all entries, not just those used.
\printglossary[type=notation, title=Mathematical Notation]

\addcontentsline{toc}{section}{Literature Cited}
\bibliography{/Users/blaine/Documents/global}

\addcontentsline{toc}{section}{Index}
\printindex

